The K2 Halo Photometry Campaign

### 2019-03-07 paper/ms.tex
orcid for bedding
tables and paper reorganized

\author{Timothy R. Bedding}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars which saturate the detector are nevertheless some of the most interesting because of the ease with which they can be observed by other instruments and the wealth of knowledge about them that is already available. By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign 6 onwards. This halo campaign reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. Here we describe our pipeline, and present a catalogue of the halo sources, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product. \href{https://github.com/benjaminpope/aselli}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!

@@

This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.

@@

\input{all_stars_1}
\input{all_stars_2}
\input{all_stars_3}
\input{all_stars_4}
\input{all_stars_5}
%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

>>>>

\author[0000-0001-5222-4661]{Timothy R. Bedding}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars which saturate the detector are nevertheless some of the most interesting because of the ease with which they can be observed by other instruments and the wealth of knowledge about them that is already available. By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign 6 onwards. This halo campaign reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. Here we describe our pipeline, and present a catalogue of the halo sources, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product. \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!

@@

This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{scipy}; \texttt{lightkurve} \citep{lightkurve}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.

@@

\input{all_stars_1}
\input{all_stars_2}
\input{all_stars_3}
\input{all_stars_4}
\input{all_stars_5}
\input{all_stars_6}

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors
